Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-21 string_jpam.tex
clarification

If, conversely, $r'(\phi)>0$ whenever~$r>1$, then the string has only
one free end; the other is tangential to the event horizon (in the
sense that ${\displaystyle \lim_{r\longrightarrow 1^+}r'=0}$), except
in the exceptional case of constant~$\phi$ when the string is radial
for~$r>1$.

>>>>

If, conversely, $r'(\phi)\neq 0$ whenever~$r>1$, then the string has
only one free end; the other is tangential to the event horizon (in
the sense that ${\displaystyle \lim_{r\longrightarrow 1^+}r'=0}$),
except in the degenerate case of constant~$\phi$ when the string is
radial for~$r>1$.
